Multi-level modeling with Openflexo/\FML

### 2021-10-07 7-requirementssatisfaction.tex
synchro

    \item \emph{Ontological instantiation} (\textit{O.Inst.}): fulfillment of a requirement is obtained by the relation between an instance and its type definition instance (for example the notion of \textit{developer} of \textbf{S3} is implemented by both a concept in \textit{Acme metamodel} and an instance in \textit{Acme model}).

@@

\noteSylvain{updated}

>>>>

    \item \emph{Ontological instantiation} (\textit{O.Inst.}): fulfillment of a requirement is obtained by the relation between an instance and its type definition instance (for example the notion of \textit{developer} of \textbf{S3} is implemented by both a concept in \textit{Acme metamodel} and an instance in \textit{Acme model}, see bottom left of Figure~\ref{fig:AcmeFullArchitecture}).

@@

%\noteSylvain{updated}
